Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Added chart by time.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\textwidth]{figures/people-sorted-time-chart.png}
\caption{A chart showing time spent per member on PeerMind, sorted by time.}
\label{fig:time}
\end{figure}

Figure~\ref{fig:time} shows time spent per member on PeerMind, sorted by time. While on average, members
spent 7002 seconds (around 2 hours) using the application, the distribution of users is fairly
long-tailed with many members only spending 30 minutes and some members spending upwards of 20 hours.
